---
title: "Online GREAT analysis"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---


Repo: https://github.com/jokergoo/jokergoo.github.io/tree/master/talks

We first read the regions (peaks of the transcription factor JUN) as a data frame.

```{r}
bed = read.table("Encode3_JUN_hg19.bed")
head(bed)
dim(bed)
```

Use `submitGreatJob()` to submit the regions to the GREAT web server. By default
the species is human (hg19). Current version of GREAT support `"hg38"`, `"hg19"`, `"mm10"`, `"mm9"`.


```{r, message = FALSE, warning = FALSE}
library(rGREAT)
job = submitGreatJob(bed)
```


The summary of the job.

```{r}
job
```

Next step is to select one or more ontology categories and to retrieve the result tables.
There are many ontologies integrated in GREAT. The total ontologies can be get by:

```{r}
availableOntologies(job)
```

By default three GO ontologies are used. 

```{r}
tbl = getEnrichmentTables(job)
```

Once the result tables are retrieved, they are cached.

```{r}
job
```

More ontologies can be set via the `ontology` argument.

```r
getEnrichmentTable(job, ontology = c("GO Biological Process", "Mouse Phenotype"))
```


`tbl` is a list of three tables and each table contains enrichment results for a GO ontology:

```{r}
names(tbl)
head(tbl[["GO Biological Process"]])
```

```{r, fig.width = 7, fig.height = 7}
plotVolcano(job, ontology = "GO Biological Process")
```

The global region-gene association plots:

```{r, fig.width = 10}
plotRegionGeneAssociationGraphs(job)
```

Or the association specifically for a specific term.

```{r, fig.width = 10}
plotRegionGeneAssociations(job, ontology = "GO Molecular Function",
    term_id = "GO:0004984")
```

The table of the associations between genes and regions.

```{r}
getRegionGeneAssociations(job, ontology = "GO Molecular Function",
    term_id = "GO:0004984")
```

Note, you cannot get the association bewteen genes and _all_ regions.
It is not supported by the web GREAT.

There is a Shiny app that contains all the results.

```{r, eval = FALSE}
shinyReport(job)
```


Bonus: If you use the GO category, you can use the **simplifyEnrichment** to summarize the results. 


```{r, message = FALSE, fig.width = 9, fig.height = 5.5}
library(simplifyEnrichment)
tb = tbl[["GO Biological Process"]]
sig_go = tb$ID[tb$Binom_Adjp_BH < 0.01]
length(sig_go)
simplifyGO(sig_go)
```


```{r}
sessionInfo()
```

